Freezing of a Weeks-Chandler-Anderson Fluid using classical Density Functional Theory

### 2020-09-08 papers/thesis-kirstie/thesis.tex
a couple cleanups

In summary, classical Density Functional Theory (cDFT) is used in conjunction with Soft Fundamental Measure Theory (SFMT) to find the equilibrium free energy of a system, and the corresponding equilibrium number density profile. In particular, SFMT is used to form the expression for the excess free energy without having to take into account the interaction each sphere, or atom, has with every other sphere. The excess free energy is then added to the ideal free energy calculated analytically to find the resulting Free energy for the system. 
\begin{equation}{F=F_{ideal} + F_{excess}}\end{equation} 
For a spatially varying number density, as would be expected for a crystal, the free energy is a functional of the number density profile $n(\vec{r})$  
\begin{equation}{F[n(\vec{r})]=F_{ideal}[n(\vec{r})] + F_{excess}[n(\vec{r})]}\end{equation} To implement cDFT, the number density profile $n(\vec{r})$ is varied with the temperature fixed until the free energy is minimized. The minimum free energy and its corresponding number density profile are then the equilibrium values for that temperature.

Once the Helmholtz free energy for both the crystal and liquid states of the fluid are found, they can be compared to find the resulting state of the fluid. Outside the region of coexistence, the fluid will be completely in a crystalline state if the crystal free energy is lower than the liquid free energy, and it will be completely in a liquid state if the liquid free energy is lower than the crystal free energy as was discussed in Section IB.

>>>>

In summary, classical Density Functional Theory (cDFT) is used in conjunction with Soft Fundamental Measure Theory (SFMT) to find the equilibrium free energy of a system, and the corresponding equilibrium number density profile. In particular, SFMT is used to form the expression for the excess free energy without having to take into account the interaction each sphere, or atom, has with every other sphere. The excess free energy is then added to the ideal free energy calculated analytically to find the resulting free energy for the system. 
\begin{equation}{F=F_{ideal} + F_{excess}}\end{equation} 
For a spatially varying number density, as would be expected for a crystal, the free energy is a functional of the number density profile $n(\vec{r})$  
\begin{equation}{F[n(\vec{r})]=F_{ideal}[n(\vec{r})] + F_{excess}[n(\vec{r})]}\end{equation} To implement cDFT, the number density profile $n(\vec{r})$ is varied with the temperature fixed until the free energy is minimized. The minimum free energy and its corresponding number density profile are then the equilibrium values for that temperature.

Once the Helmholtz free energy for both the crystal and liquid states of the fluid are found, they can be compared to find the resulting state of the fluid. Outside the region of coexistence, the fluid will be completely in a crystalline state if the crystal free energy is lower than the liquid free energy, and it will be completely in a liquid state if the liquid free energy is lower than the crystal free energy.
